Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2021-04-18 Thesis/article.tex
buOH solution general

@@

@@

In order to make a 
%double concentrated 
\gls{2f}
solution, the volume of \gls{zrpro} and \gls{acac} is doubled and \gls{buoh} is decreased by the volume of \gls{zrpro}. 

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The solvent (\gls{buoh}) is put into a beaker glass (or similar, preferably with \td{an air-tight} cap) with a stirrer and \gls{zrpro} is added while stirring.  
After 10 to 15 minutes one mole equivalent chelating agent (\gls{acac}) is added and stirred for another 10 to 15 minutes. 
Finally, the stabilisation solvent (\gls{ipo} or \gls{acoh}) is added to the mixture and stirred for additional 20-30 minutes. 

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In order to make a \gls{2f} solution, the volume of \gls{zrpro} and \gls{acac} is doubled and \gls{buoh} is decreased by the volume of \gls{zrpro}. 
